% !TeX spellcheck = en_GB
\documentclass[letterpaper]{article}
%\oddsidemargin=0.15in
%\evensidemargin=0.15in
%\textwidth=6.0in
%\topmargin=-.5in
%\textheight=9.0in
\usepackage[margin=1.5in]{geometry}
\parindent=0in

\pagestyle{empty}

\usepackage{graphicx, bbding, pifont, fontawesome, xcolor}

\let\dateshape\bf

\begin{document}
\vspace*{-2.75pc}
\begin{center}
	\scalebox{1.2}{\Huge Jacob W.F. House} \\[.75pc]
	{\Large\raisebox{-2pt}{\ding{41}}} jacob@jacobhouse.ca \quad 
	{\Large\raisebox{-1.75pt}{\ding{37}}} (941) 726-0872 \quad
	\faHome\ 2 Briarwood Place, St. John's
	\\[2pc]
\end{center}

{\large \bf Education} \\*[-.8pc]
\underline{\hspace{\textwidth}} \\[0.5pc]
{\bf B.Sc. in Computer Science, Memorial University} \hfill {\dateshape 2016-Present} \\
Term~7 academic average of 85\% (3.8 GPA). Completed a minor in Mathematics with a focus on Pure Mathematics and CS electives in operating systems, cryptography, and security. \\
\\
{\bf International Baccalaureate Diploma Programme Certificates} \hfill {\dateshape 2016} \\
Certificates in Higher Level Biology, Chemistry, European History, and in Standard 
Level Mathematics with grades of 5, 5, 5, and 6, respectively. These marks are out of 7. \\
\\
{\bf Newfoundland \& Labrador High School Diploma, Honours} \hfill {\dateshape 2016} \\
Weighted overall average: 88\% \\
\\[0.5pc]
{\large \bf Employment} \\*[-.8pc]
\underline{\hspace{\textwidth}} \\[0.5pc]
{\bf Software Developer, The Commons @ MUN } \hfill {\dateshape January 2019--Present\/} \\
I am creating a web-based mobile printing system to integrate with existing LabNet
services using Adobe Acrobat's Preflight print production toolset. \\
\\
{\bf Marketing Assistant, The Commons @ MUN } \hfill {\dateshape June 2018--December 2018\/} \\
At the Commons I created both print and digital branding material such as posters and Instagram 
ads. I also updated internal documentation including brand standards and employee profiles. \\
%At The Commons, my marketing responsibilities include creation of marketing 
%material for social media and print, as well as internal documentation. \\
\\
{\bf Sales Associate, Old Navy } \hfill {\dateshape June 2015--September 2016\/} \\
Responsibilities included positions such as cashier, shipment team, sales-floor,
and fitting rooms. Here I was known as an extremely hard-working employee whose
quality of work could always be counted on in fast-paced situations, such as 
being made head cashier in the evening on Black Friday. \\
\\[0.5pc] %\newpage
{\large \bf Volunteering} \\*[-.8pc]
\underline{\hspace{\textwidth}} \\[0.5pc]
{\bf Full Stack Developer \& Technical Producer, VOWR} \hfill {\dateshape June 2018--Present\/} \\
I volunteer at the Voice of Wesley Radio Station designing and developing a web-based music inventory system using Python and MySQL in Docker to replace an aging infrastructure. I also used to help record {\em Guest Interview} each week when school was not in session. \\
\\
{\bf IT \& Security Consultant, MUN} \hfill {\dateshape January 2017--August 2018\/} \\
Assisted patching security vulnerabilities and automated deployment of Windows 
computer-images using Memorial University's in-house LabNet image management system. \\
\\
{\bf High School Newspaper} \hfill {\dateshape 2014 to 2015\/} \\
Department Head of Design and Formatting (2014-2015), Co-Director (2015)  \\
\\[0.5pc]
{\large \bf Skills} \\*[-.8pc]
\underline{\hspace{\textwidth}} \\[0.5pc]
{\bf Computer Programming} \\
Fluent in Python, C, JavaScript, and shell scripting. Some experience with C++, Java, and Windows PowerShell. \\
\\
{\bf Server Administration} \\
Very experienced with app deployment in both Windows-, Linux, and BSD-based GUI and CLI server environments, with an interest in automation of such tasks using technologies such as Docker. \\
\\
{\bf \LaTeX\ Typesetting} \\
Professional typesetting of documentation, textbooks, and academic course notes and development of \LaTeX\ style files and classes for the MUN Computer Science Society. \\
% \\
% {\bf Photography \& Graphic Design} \\
% Moderate experience with DSLR camera photography, digital image processing, and poster, business card and stationary design.  \\
% \\
% {\bf Competitive Swimming Summer Camp Instructor} \hfill {\dateshape Summer 2014} \\
% Here my responsibilities included coordinating group activities with young children,
% facilitating a fun and effective coaching environment for my group of swimmers, as 
% well as accommodating the needs of each individual swimmer.   \\
\\[0.5pc] %\newpage
{\large \bf Awards} \\*[-.8pc]
\underline{\hspace{\textwidth}} \\[0.5pc]
{\bf MUN Faculty of Science Dean's List} \hfill {\dateshape 2016\,--\,2017 Academic Year} \\
An award presented to students who have demonstrated exceptional academic performance by ranking in the top ten per cent of undergraduate science students. \\
\\
{\bf Newfoundland Regional Science Fair, Bronze Medalist} \hfill {\dateshape 2015\/} \\
A statistical analysis of training techniques used in competitive swimming, 
entitled {\it Is Tapering Effective?} \\
\\[0.5pc] 
% {\large \bf References} \\*[-.8pc]
% \underline{\hspace{\textwidth}} \\[0.5pc]
%\\
%{\bf Name, Relationship}  \\
%Phone: (XXX) XXX-XXXX, email: email@address.com \\
%\\
\end{document}
